Programs Performance Analysis Toolkit

### 2013-10-07 keynote/Keynote.tex
Add a stub of architecture diagram
Implement some drawing

@@

@@

@@

>>>>

\usepackage{asymptote}

@@

\section{Introduction}

@@

\section{Methodology}

@@

\section{Implementation}

\begin{frame}[fragile]
\begin{center}
\begin{asy}
	unitsize(1mm);

	struct Rectangle {
		pair lb;
		pair rt;
		Label l;
		pen border;
		pen fill;

		void operator init(pair lb, pair rt, Label l="", pen border = black, pen fill = white)
		{
			this.lb = lb;
			this.rt = rt;
			this.l = l;
			this.border = border;
			this.fill = fill;
		}
	}

	struct Block {
		Rectangle rect;
		Rectangle[] childs;

		void operator init(pair lb, pair rt, Label l="", pen border = black, pen fill = white, Rectangle[] childs)
		{
			rect.operator init(lb, rt, l, border, fill);
			this.childs = childs;
		}
	}

	void draw(Rectangle r)
	{
		path p = r.lb--(r.lb.x, r.rt.y)--r.rt--(r.rt.x, r.lb.y)--cycle;
		fill(p, r.fill);
		label(r.l, ( (r.rt.x - r.lb.x) / 2 , (r.rt.y - r.lb.y) / 2 ));
		draw	(p, r.border);
	}

	void draw(Block s)
	{
		draw(s.rect);
		for (Rectangle r : s.childs) {
			draw(r);
		}
	}

	Rectangle[] rects = {Rectangle((0,0), (40,10), Label("Nested stuff"), black, lightblue)};
	draw(Block((0,0), (50,20), Label("Database server"), black, lightgreen, rects));

\end{asy}
\end{center}
\end{frame}
